Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Add type signatures

>>>>

type `data.tree::Traverse` <class<`Node`, `R6`>, character[], any, any> => list<any>;

type `emulator::cprod` <class<`matrix`> | double[], class<`matrix`> | double[]> => class<`matrix`>;

type `lava::lava.options` <...> => list<double | character[]>;

type `coin::\%GE\%` <class<`matrix`> | class<`matrix`, `pvalue`> | double[], double[] | class<`matrix`, `pvalue`>> => (class<`matrix`> | logical[]);

type `emplik::llogp` <class<`matrix`> | double[], double> => (class<`matrix`> |
double[]);

type `emplik::gradf` <class<`matrix`>, double[], double[]> => double[];

type `fields::rdist` <class<`data.frame`> | class<`matrix`> | double[], class<`data.frame`> | class<`matrix`> | null | double[], logical> => (class<`matrix`> | class<`dist`>);
